---
title: "R Markdown中文pdf输出模版"
author: "王泽贤"
date: '2016年10月8日'
################################“#“范围内请勿修改
#请确认Rmd文件和header.tex在同一个文件夹中
#header.tex可编辑，可改字体，保存时请务必保存为utf-8无BOM编码格式(在rstudio中编辑自动保存为此格式)
output: 
  pdf_document: 
    latex_engine: xelatex
    includes:
          in_header: header.tex
################################”#“范围内请勿修改
---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
这是一个R Markdown文件。 更多细节请看[rmarkdown.rstudio.com](http://rmarkdown.rstudio.com)

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## 插入图片

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## 输入公式

$$y_1=x^2+\sum{a_x}+\frac{1}{ddd}$$